Figure 2-Supplement 2

### 2018-02-12 inst/p1_hek293t/p1_hek293t.Rmd
fixing analysis with lncTAM34a name, removing violin, adding CI and mean, for p1_hek293t, again

figure <- plotPDF(p) +
  geom_linerange(
    data = stats,
    aes(
      x = shRNA, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = GOI
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = shRNA, 
      y = mean, 
      group = GOI
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    shape = 95,
    size = 6,
    show.legend = FALSE
  ) +
  theme(
    strip.text.x = element_blank(),
    axis.text.x = element_text(angle = 90)
  )

>>>>

figure <- plotPDF(p) +
  geom_linerange(
    data = stats,
    aes(
      x = shRNA, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = GOI
    ),
    colour = "grey30",
    position = position_dodge(width = 0.9),
    size = 0.3,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = shRNA, 
      y = mean, 
      group = GOI
    ),
    colour = "grey30",
    position = position_dodge(width = 0.9),
    shape = 95,
    size = 4,
    show.legend = FALSE
  ) +
  theme(
    strip.text.x = element_blank(),
    axis.text.x = element_text(angle = 90)
  )
